{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-08-01 Notebook LaTEX/Momentum Accelerations/main.tex
>w< home, work sync
>w< work home sync

@@

\section{Classical analysis of Nesterov accelerated gradient}
    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details. 
    We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm.

>>>>

                \langle \mathcal G_L(y_t), y_t - z_t\rangle. 

@@

\section{Classical analysis of Nesterov accelerated gradient}
    In this section, we reproduce some of the analysis for Nesterov accelerated gradient method with excruciating details, in the appendix. 
    We will introduce the method of estimating sequence invented by Nesterov. 
    We will also go over some details about the history, development and motivations behind the accelerated gradient algorithm. 
    \subsection{Method of Estimating Sequence}
        In this section we introduce the method of estimating sequence.
